hierarchical data

### 2025-04-07 documentation/hierarchicalmodels_seqruns.qmd
update for use in bayescoverage

```{r}
fit1a <- fit_model(runstep = "step1a",
                              hierarchical_level     =  hierarchical_level,
                              survey_df = dat,
                              chains = 4)

@@

```{r}
fit_local <- fit_model(runstep = "local_national",
                                  global_fit = fit1a,
                                  survey_df = dat,
                                  chains = 4)
```

>>>>

```{r}
fit1a <- fit_model_localhierarchy(runstep = "step1a",
                              hierarchical_level     =  hierarchical_level,
                              survey_df = dat,
                              chains = 4)

@@

```{r}
fit_local <- fit_model_localhierarchy(runstep = "local_national",
                                  global_fit = fit1a,
                                  survey_df = dat,
                                  chains = 4)
```

### 2025-04-07 documentation/hierdata.qmd
update for use in bayescoverage

We need to define the hierarchical levels to use, and the level of interest. Here we set level of interest to be equal to lowest level (iso), this is currently required (and the default setting in all runs in fit_model).

>>>>

We need to define the hierarchical levels to use, and the level of interest. Here we set level of interest to be equal to lowest level (iso), this is currently required (and the default setting in all runs in fit_model_localhierarchy).
